Discussion

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/method.Rmd
placeholder for figures
added Protocol Registration section

The newly developed ER paradigm was tested in a pilot study with $N=`r nrow(data_quest_pilot)`$ participants (`r length(which(data_quest_pilot$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the *corrugator* and *levator* compared to active viewing of negative pictures.
In accordance with our previous study[@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
All results are detailed in the [Supplementary Material](#SupplementaryMaterial), figures S1 to S7 and table S2 to S8.

@@

@@

The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CAD).

>>>>

The newly developed ER paradigm was tested in a pilot study with $N=`r nrow(data_quest_pilot)`$ participants (`r length(which(data_quest_pilot$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the *corrugator* and *levator* compared to active viewing of negative pictures.
In accordance with our previous study[@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
All results are detailed in the OSF repository (<https://osf.io/vnj8x/>).

@@

[INSERT FIGURE 2 HERE]

@@

The paradigm code, the R script for analysis, and the R Markdown file used to compile this document are available at [osf.io/vnj8x/](https://osf.io/vnj8x/).

## Protocol registration

The Stage 1 Registered Report protocol has been approved and is available at [osf.io/d6sc9/](https://osf.io/d6sc9/).
